---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

library(mmcc)
```

# mmcc
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/mmcc?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/mmcc)
[![Travis-CI Build Status](https://travis-ci.org/njtierney/mmcc.svg?branch=master)](https://travis-ci.org/njtierney/mmcc)
[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/mmcc/master.svg)](https://codecov.io/github/njtierney/mmcc?branch=master)

Tidying up MCMC output can be a real pain. There are plenty of packages that help with summarising MCMC and providing their own summaries, but sometimes _you just want a tidy datastructure_ so you can do your own thing. And quickly. 

`mmcc` provides tidying functions that return tidy data structure from mcmc.list objects. It uses `data.table` as the backend for speediness, it also provides `broom` tidiers to assist in some quick summaries.

# Installation

Install from github using:

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("njtierney/mmcc")
```


# Usingage mmcc

`mcmc_to_dt` takes an `mcmc.list` object and turns it into a `data.table` of the format:

```{r show-mmcc}
library(coda)
data(line)

head(data.frame(line$line1))
library(mmcc)

mcmc_dt <- mcmc_to_dt(line)

mcmc_dt

```


`tidy.mcmc.list` takes an `mcmc.list`, turns it into a `data.table` and summarises it in terms of each parameter's mean, median, standard deviation and credible interval with level given by `conf.level`:

``` {r show-tidy-method}
tidy(line)
```

We can also optionally ask for a subset of the parameters with a vector of `colnames` and summarise for each chain:

``` {r show-tidy-options}
tidy(line, 
     chain = TRUE, 
     colnames=c("alpha"))
```

This may be useful if we want to make a plot that shows how a given parameter varies from chain to chain.

``` {r show-tidy-ggplot, fig.height=3, fig.width=7}
library(ggplot2)

line_tidy <- tidy(line, chain = TRUE)

ggplot(data = line_tidy, 
       aes(x = factor(chain), 
           y = mean)) +
    geom_pointrange(aes(ymin = `2.5%`,
                        ymax = `97.5%`)) +
    facet_wrap(~parameter, 
               nrow = 1, 
               scales = "free_y") +
    theme_bw() +
    xlab("Chain") +
    ylab("Value")
```

# Why mmcc?

Full credit does to [Sam Clifford](https://www.samclifford.info/) for the name. 

To quote Sam:

> ...it's all about reshaping and manipulating mcmc chains...

...therefore, mmcc

# Future work

- Create summaries for each parameter
- Perform diagnostic summaries for convergence
- provide a suite of plotting in plotly, for speed, and interactivity.

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
