---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

library(mmcc)
```

# mmcc
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/mmcc?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/mmcc)
[![Travis-CI Build Status](https://travis-ci.org/njtierney/mmcc.svg?branch=master)](https://travis-ci.org/njtierney/mmcc)
[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/mmcc/master.svg)](https://codecov.io/github/njtierney/mmcc?branch=master)

**License:** [MIT](https://opensource.org/licenses/MIT)

<<<<<<< Updated upstream
dsmcmc provides custom functions written in data.table for tidying up mcmc.list objects.
=======
<<<<<<< Updated upstream
ds mcmc provides custom functions written in data.table for tidying up mcmc.list objects.
=======
mmcc provides custom functions written in data.table for tidying up mcmc.list objects.
>>>>>>> Stashed changes
>>>>>>> Stashed changes

``` {r, warning=F, message=F}
library(dsmcmc)
```

At this stage there are just two functions `mcmc_to_dt` that takes an `mcmc.list` object and turns it into a `data.table` of the format:

<<<<<<< Updated upstream
```{r show-dsmcmc}
=======
<<<<<<< Updated upstream
``` {r}
=======
```{r show-mmcc}
>>>>>>> Stashed changes
>>>>>>> Stashed changes
library(coda)
data(line)

head(data.frame(line$line1))

<<<<<<< Updated upstream
library(dsmcmc)
=======
<<<<<<< Updated upstream
=======
library(mmcc)
>>>>>>> Stashed changes
>>>>>>> Stashed changes
mcmc_to_dt(line)

```


and `tidy.mcmc.list` which takes an `mcmc.list`, turns it into a `data.table` and summarises it in terms of each parameter's mean, median, standard deviation and credible interval with level given by `conf.level`:

``` {r}
tidy.mcmc.list(line)
```

We can also optionally ask for a subset of the parameters with a vector of `colnames` and summarise for each chain:

``` {r}
tidy.mcmc.list(line, chain = TRUE, colnames=c("alpha"))
```

This may be useful if we want to make a plot that shows how a given parameter varies from chain to chain

``` {r, fig.height=3, fig.width=7}
library(ggplot2)

line_tidy <- tidy.mcmc.list(line, chain = TRUE)

ggplot(data=line_tidy, aes(x=factor(chain), y=Mean)) +
    geom_pointrange(aes(ymin = `2.5%`,
                        ymax = `97.5%`)) +
    facet_wrap( ~ parameter, nrow = 1, scales="free_y") +
    theme_bw() +
    xlab("Chain") +
    ylab("Value")
```

# Installation

Install from github using:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("njtierney/mmcc")
```

# Why mmcc?

Full credit does to [Sam Clifford](https://samclifford.info/) for the name. 

To quote Sam:

> ...it's all about reshaping and manipulating mcmc chains...

...therefore, mmcc

# Future work

- Create summaries for each parameter
- Perform diagnostic summaries for convergence
- provide a suite of plotting in plotly, for speed, and interactivity.

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
