---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

library(mmcc)
```

# mmcc

<!-- badges: start -->
[![R-CMD-check](https://github.com/njtierney/mmcc/workflows/R-CMD-check/badge.svg)](https://github.com/njtierney/mmcc/actions)
[![Codecov test coverage](https://codecov.io/gh/njtierney/mmcc/branch/master/graph/badge.svg)](https://codecov.io/gh/njtierney/mmcc?branch=master)
<!-- badges: end -->


Tidying up MCMC output can be a real pain. There are plenty of packages that help with summarising MCMC and providing their own summaries, but sometimes _you just want a tidy data structure_ so you can do your own thing. And quickly. 

`mmcc` provides tidying functions that return tidy data structure from mcmc.list objects. It uses `data.table` as the backend for speediness, it also provides `broom` tidiers to assist in some quick summaries.

# Installation

Install from github using:

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("njtierney/mmcc")
```


# Using mmcc

`mcmc_to_dt` takes an `mcmc.list` object and turns it into a `data.table` of the format:

```{r show-mmcc}
library(coda)
data(line)

head(data.frame(line$line1))
library(mmcc)

mcmc_dt <- mcmc_to_dt(line)

mcmc_dt

```

`tidy.mcmc.list` takes an `mcmc.list`, turns it into a `data.table` and summarises it in terms of each parameter's mean, median, standard deviation and credible interval with level given by `conf.level`:

``` {r show-tidy-method}
tidy(line)
```

We can also optionally ask for a subset of the parameters with a vector of `colnames` and summarise for each chain:

``` {r show-tidy-options}
tidy(line, 
     chain = TRUE, 
     colnames=c("alpha"))
```

This may be useful if we want to make a plot that shows how a given parameter varies from chain to chain.

``` {r show-tidy-ggplot, fig.height=3, fig.width=7}
library(ggplot2)

line_tidy <- tidy(line, chain = TRUE)

ggplot(data = line_tidy, 
       aes(x = factor(chain), 
           y = mean)) +
    geom_pointrange(aes(ymin = `2.5%`,
                        ymax = `97.5%`)) +
    facet_wrap(~parameter, 
               nrow = 1, 
               scales = "free_y") +
    theme_bw() +
    xlab("Chain") +
    ylab("Value")
```

# Helpers

`mmcc` provides helpers to extract the number of chains, iterations, simulations, and variables in an MCMC object:

```{r n-helpers}
n_chain(line)
n_iter(line)
n_sims(line)
n_var(line)
```

# glance helper

General model summary providing information on:

* Number of chains
* Number of iterations
* Number of variables/parameters
* Lower and upper effective sample size (ESS)
* lower and upper estimates of rhat measurement of convergence assessment

```{r}
glance(line)
```

# Diagnostics

```{r diagnostics}
diag_autocorr(line)
diag_ess(line)
diag_mc_stderr(line)
```

# Thinning

```{r thinning}
thin_dt(mcmc_to_dt(line), thin = 10)
```

# Why the name, "mmcc"?

Full credit does to [Sam Clifford](https://www.samclifford.info/) for the name. 

To quote Sam:

> ...it's all about reshaping and manipulating mcmc chains...therefore, mmcc

# Future work

- Summaries for each parameter
- More diagnostic summaries for convergence

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
