---
title: "Model summaries for a Bayesian linear regression"
author: "Sam Clifford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "README-"
)

library(dsmcmc)
```

First, we simulate some data

``` {r}
N <- 20
x <- sort(runif(n = N))
y <- rnorm(n=N, mean = 2*x + 1, sd=0.25)
```

We will fit the model, and therefore generate the `mcmc_object` with the `rjags` package.

``` {r}
library(rjags)
model <- jags.model(file = "model.txt",
                    data = list(n = N,
                                x = x,
                                y = y))
```

Draw burn-in samples and posterior inference samples for all terms in the model.

``` {r}
burn <- jags.samples(model,
                     c("beta.0", "beta.1", "tau.y", "mu"),
                     n.iter = 5000)

samples <- coda.samples(model,
                        c("beta.0", "beta.1", "tau.y", "mu", "y.rep"),
                        n.iter = 10000)

```

We can now convert the posterior samples to a data table and summarise the regression parameters

``` {r}
library(dsmcmc)

samples_dt <- mcmc_to_dt(samples)
samples_dt

tidy.mcmc.list(samples, conf.level=0.95, colnames = c("beta.0", "beta.1", "tau.y"))
```

Summarise the line of best fit, `mu`, and the predictions, `y.rep`,

``` {r}
mu_dt <- tidy.mcmc.list(samples, conf.level=0.95, colnames =  "mu")
y_dt <- tidy.mcmc.list(samples, conf.level=0.95, colnames =  "y.rep")
```

For convenience, add the data to these data tables for plotting

``` {r}
mu_dt[, c("x","y") := list(x, y) ]
y_dt[ , c("x","y") := list(x, y) ]
```

Now we'll generate a plot that shows the data, a 95% prediction interval and a 95% confidence interval for the means.

``` {r}
library(ggplot2)
ggplot(data=mu_dt,
       aes(x=x, y=y)) +
    geom_point() +
    geom_ribbon(aes(ymin = `2.5%`,
                    ymax = `97.5%`),
                fill = "salmon",
                alpha = 0.5) +
    geom_ribbon(aes(ymin = `2.5%`,
                    ymax = `97.5%`),
                fill = "lightskyblue",
                alpha = 0.25,
                data = y_dt) +
    geom_line(aes(y = Mean)) +
    theme_bw()
```
